FireSim2019_ManuscriptFigures

### 2023-05-26 Manuscript-figures.Rmd
Editing figure numbers to match manuscript

# Rel abundance adjusted by copy num, Figure 5 -----
See "Merged_paper_figures_Revision_GitHub.R" script

# Total trait abun by BC dissimilarity, Figure 6 -----
See "Merged_paper_figures_Revision_GitHub.R" script

# Supplementary
```{r}
# Carbon and nitrogen loss, Figure S2 -----
pChange_C <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
  geom_boxplot(aes(x=burn.trtmt, y = percent.total.C, fill = horizon), alpha = 0.7, varwidth = FALSE) + 
    theme_bw()+
  labs(x= 'Burn treatment',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Total C (%)',
       fill = 'Soil horizon') + 
  scale_fill_manual(values = c('black','grey90'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  scale_x_discrete(limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = '',
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

@@

test <- aov(percent.total.N ~ burn.trtmt, data = subset(df.meta, incub.trtmt == 'SI' & horizon == 'O'))
summary(test)
TukeyHSD(test)

# C remaining as fraction of total, Figure S3, S4 -----
#   See incubations_microbial_respiration.R
# Full ordination, Fig. S6 ----
ps.full.dataset <-readRDS('../../../CombinedFireSim1519/ps.1519FireSim.merged')
tree <- ape::read.tree('../../../CombinedFireSim1519/tree/merged-exported-tree/tree.nwk')

@@

p1

# BC dissimilarity and pH change, Figure S7-----
df.distances <- read.csv('../../data/bray-curtis-dissimilarites.csv')

# plot: Dry soil burns
p3=ggplot(subset(df.distances, incub.trtmt == 'LIwA' & burn.trtmt == 'dry'),
         aes(x=change.pH, y = BC.distance.btw.burned.and.control, color = horizon, shape = horizon)) + 
  geom_point(size=3, alpha = 0.8) +
  theme_bw() +
  facet_wrap(~horizon,ncol=2,
             labeller = labeller(horizon = HorizonLabels),
             scales = 'fixed') + 
  labs(x = expression(Delta~'pH with burning'),
       y = 'Bray-Curtis dissimilarity \ncompared to control', 
       color = 'Soil horizon',
       shape = 'Soil horizon') + 
  scale_color_manual(values = c("darkgreen","grey70"),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  scale_shape_manual(values = c('circle','triangle'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  theme(axis.title.x = element_text(size=14, margin = margin(t=10)),
        axis.title.y = element_text(size=14, margin = margin(r=10)),
        axis.text = element_text(size=12),
        legend.title = element_text(size=14),
        legend.text = element_text(size=14),
        strip.text = element_text(size=14),
        panel.spacing.x = unit(2, "lines"),
       legend.position = 'right') +
  stat_smooth(data = subset(df.distances, incub.trtmt == 'LIwA' & burn.trtmt == 'dry' & horizon == 'O'),
              method=lm,se = FALSE,color='black') +
    ylim(0,1)

# Respiration rate figures, S8, S9, S10-----
#   See "incubations_microbial_respiration.R" script

# Traits as fraction of total reads in lab data, Figure S11-----
df <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv')

@@

>>>>

# Total trait abun by BC dissimilarity, Figure 5 -----
See "Merged_paper_figures_Revision_GitHub.R" script

#### Extended data figures
```{r}
# Carbon and nitrogen loss, Extended data Figure 1 -----
pChange_C <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
  geom_boxplot(aes(x=burn.trtmt, y = percent.total.C, fill = horizon), alpha = 0.7, varwidth = FALSE) + 
    theme_bw()+
  labs(x= 'Burn treatment',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Total C (%)',
       fill = 'Soil horizon') + 
  scale_fill_manual(values = c('black','grey90'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  scale_x_discrete(limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = '',
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

@@

test <- aov(percent.total.N ~ burn.trtmt, data = subset(df.meta, incub.trtmt == 'SI' & horizon == 'O'))
summary(test)
TukeyHSD(test)
```

# C remaining as fraction of total, Extended data Figure S2, S3 -----
See incubations_microbial_respiration.R

# Decay model parameters for post-fire environment affinity incubation, Extended Data Figure 4 -----

XXXX

```{r}
# Full ordination, Extended Data Figure 5 ----
ps.full.dataset <-readRDS('../../../CombinedFireSim1519/ps.1519FireSim.merged')
tree <- ape::read.tree('../../../CombinedFireSim1519/tree/merged-exported-tree/tree.nwk')

@@

p1
```

# Rel abundance adjusted by weighted mean predicted 16S copy num, Extended Data Figure 6 -----
See "Merged_paper_figures_Revision_GitHub.R" script

# Respiration rate for lab-incubated soils, Extended data Figure 7-----
See "incubations_microbial_respiration.R" script

```{r}
# Traits as fraction of total reads in lab data, Extended data Figure 8-----
df <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv')

@@

# Extended Data Figure 9, Respiration rates with/without inocubation
See "incubations_microbial_respiration.R" script

#### Supplementary Figure 1 
```{r}
# BC dissimilarity and pH change, Supplementary Figure 1 -----
df.distances <- read.csv('../../data/bray-curtis-dissimilarites.csv')

# plot: Dry soil burns
p3=ggplot(subset(df.distances, incub.trtmt == 'LIwA' & burn.trtmt == 'dry'),
         aes(x=change.pH, y = BC.distance.btw.burned.and.control, color = horizon, shape = horizon)) + 
  geom_point(size=3, alpha = 0.8) +
  theme_bw() +
  facet_wrap(~horizon,ncol=2,
             labeller = labeller(horizon = HorizonLabels),
             scales = 'fixed') + 
  labs(x = expression(Delta~'pH with burning'),
       y = 'Bray-Curtis dissimilarity \ncompared to control', 
       color = 'Soil horizon',
       shape = 'Soil horizon') + 
  scale_color_manual(values = c("darkgreen","grey70"),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  scale_shape_manual(values = c('circle','triangle'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  theme(axis.title.x = element_text(size=14, margin = margin(t=10)),
        axis.title.y = element_text(size=14, margin = margin(r=10)),
        axis.text = element_text(size=12),
        legend.title = element_text(size=14),
        legend.text = element_text(size=14),
        strip.text = element_text(size=14),
        panel.spacing.x = unit(2, "lines"),
       legend.position = 'right') +
  stat_smooth(data = subset(df.distances, incub.trtmt == 'LIwA' & burn.trtmt == 'dry' & horizon == 'O'),
              method=lm,se = FALSE,color='black') +
    ylim(0,1)
```
